---
title: "My dynamic report"
output: html_fragment
---
## Analysis of lecture attendance, engagement and duration
This report analyses lecture engagement based on lecture duration and attendance type. 

## variables

 - **lecture attendance type**: how the lecture was attended e.g. online(recording) or in-person  attendance. 
 - **lecture engagement**: how engaging the lecture was, using an engagement score from 1(not engaging) to 5(very engaging). 
 - **lecture duration**: how long the lecture was (measured in hours)
 
## This report aims to
 
 - analyse how engagement levels differed across attendance types e.g. does engagement vary depending on whether the lecture was attended in-person or online?
 - analyse distribution of attendance modes 
 - analyses distribution of lecture duration (hours)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

```

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRFsCrKJ-8u7E1N8f9triPoKcm-ACK3IsJOKvVY3V4mvby5FgKeSzpLB8wJOOTxHqpWGEDpRpI_QDi6/pub?output=csv", show_col_types = FALSE)

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    lecture_hours = `How long was the lecture? (hours)`,
    attendance_mode = `How did you attend the lecture?`,
    engagement = `How engaging was the lecture?`
  )

latest_data$engagement <- as.factor(latest_data$engagement)
```


This section is a summary of the minimum, maximum and mean duration of lectures. This section analyses how engagement differs across attendance modes, which provides a mean engagement level for each mode of attendance. 
```{r}
# summary values 
paste("Min hours:", round(min(latest_data$lecture_hours, na.rm = TRUE), 2),
      "| Max hours:", round(max(latest_data$lecture_hours, na.rm = TRUE), 2),
      "| Mean hours:", round(mean(latest_data$lecture_hours, na.rm = TRUE), 2))

# mean engagement level
paste("Mean engagement:", round(mean(as.numeric(latest_data$engagement), na.rm = TRUE), 2))

latest_data %>%
  group_by(attendance_mode) %>%
  summarise(mean_engagement = round(mean(as.numeric(engagement), na.rm = TRUE), 2)) %>%
  mutate(comment = paste(attendance_mode, "had a mean engagement of", mean_engagement)) %>%
  pull(comment)
```


Graph 1 displays the distribution of lectures attended in-person and lecture recordings watched online. 

```{r}
# lecture attendance plot - plot 1
latest_data %>%
  ggplot() +
  geom_bar(aes(y = attendance_mode, fill = attendance_mode)) +
  labs(
    title = "How the Lecture was Attended",
    x = "Number of Lectures",
    y = "Attendance Mode",
    fill = "Attendance Mode",
    caption = "Source: STATS 220 survey")
```


Graph 2 displays the distribution of engagement levels, ranging from 1 to 5. 

```{r}
# lecture engagement plot - plot 2
latest_data %>%
  ggplot() +
  geom_bar(aes(y = engagement, fill = as.factor(engagement))) +
  labs(
    title = "How Engaging was the Lecture?",
    x = "Number of Lectures",
    y = "Engagement Level",
    fill = "Engagement Level",
    caption = "Source: STATS 220 survey")
```


Graph 3 displays the relationship between engagement and attendance mode. 
The figure exhibits how engagement differs based on whether the lecture was attended in-person or watched online. 

```{r}
# engagement based on attendance plot - plot 3
latest_data$engagement <- as.factor(latest_data$engagement)
latest_data %>%
  ggplot(aes(x = attendance_mode, fill = engagement)) +
  geom_bar() +
  labs(
    title = "Engagement level by Attendance Mode",
    x = "Attendance mode",
    y = "Number of lectures",
    fill = "Engagement level",
    caption = "Source: STATS 220 survey")
```


```{css}
body {
  font-family: Courier, sans-serif;
  background-color: #FFFFC5;
}
```

## What's going on with this data?

This section is an analysis of mean length duration (measured in hours) and mean levels of engagement, measured on a scale from 1 - least engagement, to 5 - most engagement.
```{r}
paste(
  "The mean lecture duration was",
  round(mean(latest_data$lecture_hours, na.rm = TRUE), 2),
  "hours and the mean level of engagement was",
  round(mean(as.numeric(latest_data$engagement), na.rm = TRUE), 2)
)
```


This section is an analysis of the minimum and maximum lecture duration (in hours). 

```{r}
latest_data %>%
  summarise(
    min_hours = min(lecture_hours, na.rm = TRUE),
    max_hours = max(lecture_hours, na.rm = TRUE)
  ) %>%
  mutate(
    comment = paste(
      "Lecture duration ranged from",
      round(min_hours, 2),
      "to",
      round(max_hours, 2),
      "hours."
    )
  ) %>%
  pull(comment)
```


This section displays a comparison between mean engagement levels for in-person lecture attendance and online lecture attendance.

```{r}
latest_data %>%
  group_by(attendance_mode) %>%
  summarise(
    mean_engagement = round(mean(as.numeric(engagement), na.rm = TRUE), 2)
  ) %>%
  mutate(comment = paste(attendance_mode, "had a mean engagement of", mean_engagement)) %>%
  pull(comment)
```